Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-02-04 causal-bandit/icml-2015/discussion.tex
Re-org discussion

Both our general causal model algorithm and algorithm for parallel bandits are adaptive reward estimators.

@@

%

@@

\cite{wu2015online} consider a relevant feedback model.

\subsection{Open Questions}

\paragraph{General graphs with known structure but latent variables}
In this case, some queries will be non-identifiable. The corresponding actions can be immediately added to the set $A$ prior to collecting any data. We can then use the same algorithm as in the case where there are no latent variables, except that we will have to use the more general do-calculus rather than simply adjusting for the parents to write the expression for each action in terms of observational data.

\paragraph{Graphs with partially or unknown structure}

\begin{itemize}

\item Unknown in general case - e.g., like algorithm 1

\item Partially known structure
There has been substantial work on the problem of selecting experiments to discover the correct causal graph from within a Markov equivalence class \cite{Eberhardt2005,eberhardt2010causal,hauser2014two,Hu2014}. This problem arises naturally if we assume free access to a large observational dataset, from which the Markov equivalence class can be found via causal discovery techniques. Key results $bigo(n)$ singleton or $bigo(log log n)$ multi-variate experiments are required.
- Focus on minimizing the number of experiments that must be performed. Examples of active versus online learning. The cost of experiments constant or at least known.

\item Unknown Structure
If we need to learn the structure, in an online environment. 
Experiment is much, much more revealing than inference from observational data. We would expect it to dominate.

\end{itemize}

>>>>

Both our general causal model algorithm and algorithm for parallel bandits adaptively estimate the reward for allowable actions over $T$ rounds.
For general causal bandit problem with $N$ allowable interventions we have shown that Algorithm~\ref{alg:general} has simple regret that is never worse than $\bigo{\sqrt{N/T}}$.

\paragraph{Cumulative Regret}
In the special case of parallel bandits, we were able to remove the assumption that the conditional model

Cumulative regret... use \citep{wu2015online} to get optimal cumulative regret bound (should be $\Omega(T^{2/3})$?)

General discussion of how to map parallel bandit problem to graph feedback.

@@

\paragraph{Causal Models with Non-Observable Variables}
In this case, some queries will be non-identifiable. The corresponding actions can be immediately added to the set $A$ prior to collecting any data. We can then use the same algorithm as in the case where there are no latent variables, except that we will have to use the more general do-calculus rather than simply adjusting for the parents to write the expression for each action in terms of observational data. 
%

@@

\paragraph{Partially or Completely Unknown Causal Graph}

Unknown in general case - e.g., like algorithm 1

(Partially known structure)
There has been substantial work on the problem of selecting experiments to discover the correct causal graph from within a Markov equivalence class \cite{Eberhardt2005,eberhardt2010causal,hauser2014two,Hu2014}. This problem arises naturally if we assume free access to a large observational dataset, from which the Markov equivalence class can be found via causal discovery techniques. Key results $bigo(n)$ singleton or $bigo(log log n)$ multi-variate experiments are required.
- Focus on minimizing the number of experiments that must be performed. Examples of active versus online learning. The cost of experiments constant or at least known.

(Unknown Structure)
If we need to learn the structure, in an online environment. 
Experiment is much, much more revealing than inference from observational data. We would expect it to dominate.
